### 2018-01-22 mcmc.tex
typos

Importantly---for the algorithm given above to work correctly---the
  proposal pdf must satisfy a ``detailed-balance'' condition\footnote{This
  detailed-balance condition in \equationname~(\ref{eq:detailed-balance})
  requires implicitly that the function $q(\pars'\given\pars)$ is also
  properly normalized. That is, that it integrates (over $\pars'$) to unity
  for any setting of $\pars$. That is an extremely technical point, but stands
  as a reminder that you don't want to mess with detailed balance casually!};
  it must have the property that
\begin{eqnarray}
q(\pars'\given\pars) &=& q(\pars\given\pars')
\label{eq:detailed-balance}\quad ;
\end{eqnarray}
that is, it must be just as easy to go one way in the parameter space
  as the other.
You can break this property, if you like, and then adjust the
  acceptance condition accordingly (which is truly the Metropolis--Hastings algorithm), but we \emph{do not recommend this}
  except under the supervision of a trained professional.\note{Actually,
  our own favorite method, \project{emcee}, has a proposal pdf that does
  violate detailed balance in this way and has a compensated
  acceptance probability.  Read the paper \cite{emcee} for more details.}
The reason is:  It is one thing to draw samples from $q(x'\given x)$.
It is another thing to correctly write down $q(x'\given x)$.
  If you violate detailed balance in $q(x'\given x)$ then you have to be
  able to \emph{both} draw from \emph{and} write down $q(x'\given x)$
  and you are subject to a set of new possible bugs for your code.
If the detailed balance condition frightens you (as it frightens us),
  then just stick with pdfs that are symmetric in $\pars'$ and $\pars$,
  like the Gaussian, or a centered uniform distribution, and forget about
  it.

@@

The second---and less important---point about model checking is that
the ur-Bayesian thing to be doing is computing a Bayesian evidence
integral.
However, it is usually inadvisable:
The integral is expensive to compute.
Most \MCMC\ methods are cleverly designed to \emph{avoid} computing this
integral (as we note above in \sectionname~\ref{sec:when}); so it usually adds
expense to the project.
At the end of the day, it returns only a single, scalar number, with
no guidance about how to use it (and indeed there are only heuristics
to reach for).
If your model is wrong, the richer tests of visualization of residuals
or sensitivity to assumptions are much more likely to lead to insight
about what changes to make or what new directions to explore.\footnote{%
  There is a growing idea that Bayesian inference---and inference in general---is
  about much more than inferring parameter values: It is about understanding and
  elaborating models (for example, \citealt{gabry}).}

>>>>

Importantly---for the algorithm given above to work correctly---the
  proposal pdf must satisfy a ``detailed-balance'' condition\note{This
  detailed-balance condition in \equationname~(\ref{eq:detailed-balance})
  requires implicitly that the function $q(\pars'\given\pars)$ is also
  properly normalized. That is, that it integrates (over $\pars'$) to unity
  for any setting of $\pars$. That is an extremely technical point, but stands
  as a reminder that you don't want to mess with detailed balance casually!};
  it must have the property that
\begin{eqnarray}
q(\pars'\given\pars) &=& q(\pars\given\pars')
\label{eq:detailed-balance}\quad ;
\end{eqnarray}
that is, it must be just as easy to go one way in the parameter space
  as the other.
You can break this property, if you like, and then adjust the
  acceptance condition accordingly (which is truly the Metropolis--Hastings algorithm), but we \emph{do not recommend this}
  except under the supervision of a trained professional.\note{Actually,
  our own favorite method, \project{emcee}, has a proposal pdf that does
  violate detailed balance in this way and has a compensated
  acceptance probability.  Read the paper \cite{emcee} for more details.}
The reason is:  It is one thing to draw samples from $q(x'\given x)$.
It is another thing to correctly write down $q(x'\given x)$.
  If you violate detailed balance in $q(x'\given x)$ then you have to be
  able to \emph{both} draw from \emph{and} write down $q(x'\given x)$
  and you are subject to a set of new possible bugs for your code.
If the detailed balance condition frightens you (as it frightens us),
  then just stick with pdfs that are symmetric in $\pars'$ and $\pars$,
  like the Gaussian, or a centered uniform distribution, and forget about
  it.

@@

The second---and less important---point about model checking is that
the ur-Bayesian thing to be doing is computing a Bayesian evidence
integral.
However, it is usually inadvisable:
The integral is expensive to compute.
Most \MCMC\ methods are cleverly designed to \emph{avoid} computing this
integral (as we note above in \sectionname~\ref{sec:when}); so it usually adds
expense to the project.
At the end of the day, it returns only a single, scalar number, with
no guidance about how to use it (and indeed there are only heuristics
to reach for).
If your model is wrong, the richer tests of visualization of residuals
or sensitivity to assumptions are much more likely to lead to insight
about what changes to make or what new directions to explore.\note{%
  There is a growing idea that Bayesian inference---and inference in general---is
  about much more than inferring parameter values: It is about understanding and
  elaborating models (for example, \citealt{gabry}).}
